Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-13 ieee_paper.tex
minor + using pdf figures

\documentclass[10pt, conference, compsocconf]{IEEEtran}
\input{support/macros} % color is defined in macros or misc_mac
\input{support/misc_mac}
\input{support/setupicase}

@@

\def\qes#1{}
\def\es#1{}
\def\ge#1{}
\usepackage{morefloats}

\usepackage{graphicx}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{fixltx2e}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{\IEEEauthorblockN{Gordon Erlebacher\IEEEauthorrefmark{1},
Erik Saule\IEEEauthorrefmark{2}, Natasha Flyer\IEEEauthorrefmark{3}, 
and Evan Bollig\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Scientific Computing, 
Florida State University, Tallahassee, FL 32306-4120\\
Email: gerlebacher@fsu.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Computer Science, University of North Carolina at Charlotte\\
Email: erik.saule@uncc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Computational and Information Systems Laboratory, UCAR \\
Email: 
flyer@ucar.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Department of Scientific Computing, Florida State University\\
Email: bollig@gmail.com}}
\maketitle

@@

\newfig{figures/gflops_peak.png}{2.5in}{Peak performance of SpMV algorithm assuming either 1 or 4 matrices and/or vectors. We used a memory bandwidth of 150 Gbytes/sec (based on measurements in a code similar to the SpMV kernel, with computations removed.)}{fig:gflops_peak_perf}

\newfig{figures/speedup_wrt_base.png}{\wide}{Speedup relative to base case using one matrix and one vector.}{fig:speedup}

@@

\newfig{figures/swizzling.pdf}{\wide}{Duplication of the first four bytes of each channel across the entire channel.}{fig:swizzling}
\newfig{figures/channel_permutation.pdf}{\wide}{Channel Permutations on the MIC}{fig:permutation}
\newfig{figures/tensor_product.pdf}{\wide}{Tensor scalar product using channels and swizzling.}{fig:tensor_product}

@@

>>>>

\documentclass[10pt,conference,compsocconf]{IEEEtran}
\input{support/macros} % color is defined in macros or misc_mac
\input{support/misc_mac}
\input{support/setupicase}

@@

\def\qes#1{}
\def\es#1{}
\def\ge#1{}
%\usepackage{morefloats}

\usepackage[pdftex]{graphicx}
\usepackage{subfigure}
%\usepackage{fixltx2e}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{\IEEEauthorblockN{Gordon Erlebacher\IEEEauthorrefmark{1},
Erik Saule\IEEEauthorrefmark{2}, Natasha Flyer\IEEEauthorrefmark{3}, 
and Evan Bollig\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Scientific Computing, 
Florida State University, Tallahassee, FL 32306-4120\\
Email: gerlebacher@fsu.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Computer Science, University of North Carolina at Charlotte\\
Email: esaule@uncc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Computational and Information Systems Laboratory, UCAR \\
Email: flyer@ucar.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Department of Scientific Computing, Florida State University\\
Email: bollig@gmail.com}}
\maketitle

@@

\newfig{figures/gflops_peak.pdf}{2.5in}{Peak performance of SpMV
  algorithm assuming either 1 or 4 matrices and/or vectors. We used a
  memory bandwidth of 150 Gbytes/sec (based on measurements in a code
  similar to the SpMV kernel, with computations
  removed.)}{fig:gflops_peak_perf}

\newfig{figures/speedup_wrt_base.pdf}{\wide}{Speedup relative to base
  case using one matrix and one vector.}{fig:speedup}

@@

\newfig{figures/swizzling.pdf}{\wide}{Duplication of the first four
  bytes of each channel across the entire channel.}{fig:swizzling}

\newfig{figures/channel_permutation.pdf}{\wide}{Channel Permutations
  on the MIC}{fig:permutation}

\newfig{figures/tensor_product.pdf}{\wide}{Tensor scalar product using
  channels and swizzling.}{fig:tensor_product}

@@

\begin{figure*}[t]
  \centering
  \subfigure[a]{\includegraphics[width=.49\linewidth]{figures/supercompact_max_perf.pdf}}
  \subfigure[b]{\includegraphics[width=.49\linewidth]{figures/compact_max_perf.pdf}}

  \subfigure[c]{\includegraphics[width=.49\linewidth]{figures/random_max_perf.pdf}}
  \subfigure[d]{\includegraphics[width=.49\linewidth]{figures/rbf_max_perf_run1.pdf}}
  \caption{perf accross instance types}
\end{figure*}
